---
title: "PDS Intro"
author: "Paul"
date: "2023-09-15"
output: pdf_document
---


```{r}
library(ncdf4)
library(DataExplorer)
library(plotly)
library(tidyverse)
library(plotly)
library(data.table)
```

# Load Data

```{r}
flux <- nc_open("/Users/welpp/Desktop/Practical Data Science/Data/flux")
daily <- nc_open("/Users/welpp/Desktop/Practical Data Science/Data/daily")
flare <- nc_open("/Users/welpp/Desktop/Practical Data Science/Data/flare")
```


# Flux

## Munge & Info


```{r}
time_flux <- flux$dim$time$vals
time_unit_flux <- flux$dim$time$units

var_names <- names(flux$var)
## var_names

var_names_flux <- var_names[-c(15,16)]
## var_names_flux

for (i in var_names_flux){
  name <- paste("", i, sep = "")
  assign(name, ncvar_get(flux, varid = i))
}


flux_df <- data.frame(lapply(mget(var_names_flux), as.vector))
flux_df <- cbind(time_flux, flux_df)

reference_time <- min(flux_df$time_flux)
flux_df$time_flux <- as.POSIXct("2000-01-01 12:00:00", tz="UTC") + (flux_df$time_flux)

## flux_df$time_flux
```

time_flux: time (in UTC)

xrsa_ <- x-ray sensor
   0.05 to 0.4 nm (Channel A)
    0.1 to 0.8 nm (Channel B)
    ”1” denotes the low-irradiance sensor
    ”2” denotes the high-irradiance sensor
    
_primary_chan: indicates whether XRS-A1 or XRS-A2 provides the primary irradiance values

_flag: i presume flags of when it is a solar flare???? particle spikes????

au_factor: The AU factor is a unitless scaling factor used to convert pixel coordinates or image measurements into physical units, such as kilometers or solar radii, when analyzing solar images taken by spacecraft. It helps in determining the size or distance of features observed on the solar disk. The actual value of the AU factor can vary depending on the specific instrument or mission, and it is often provided in the metadata of solar image data.

roll_angle: The roll angle is an orientation parameter that represents the rotation of a spacecraft or satellite around its longitudinal (roll) axis. In the context of solar observations, it is used to specify the orientation of the spacecraft relative to the Sun. Solar observatories like SOHO and SDO may need to adjust their roll angle to keep the solar target within the field of view of their instruments. The roll angle is typically given in degrees and can change over time as the spacecraft orbits and reorients itself.

yaw_flip_flag: The yaw flip flag is a binary indicator that denotes whether a spacecraft has undergone a yaw flip maneuver. A yaw flip maneuver is a deliberate change in the spacecraft's orientation where it flips or rotates about its radial (yaw) axis. This maneuver may be performed to maintain proper instrument orientation or for other operational reasons. The yaw flip flag helps track whether such a maneuver has occurred during a mission and can be useful for data interpretation.


## EDA

```{r}
gp1 <- ggplot(flux_df, aes(x = time_flux)) +
  geom_line(aes(y = xrsa_flux), color = "red", alpha = 0.2) +
  geom_line(aes(y = xrsa1_flux), color = "darkred", alpha = 0.2) +
  geom_line(aes(y = xrsa2_flux), color = "salmon", alpha = 0.2) +
  geom_line(aes(y = xrsb_flux), color = "blue", alpha = 0.2) +
  geom_line(aes(y = xrsb1_flux), color = "darkblue", alpha = 0.2) +
  geom_line(aes(y = xrsb2_flux), color = "lightblue", alpha = 0.2) +
  theme_minimal() +
  theme(legend.title = element_blank())

gp1

ggplotly(gp1)
```

```{r}
introduce(flux_df)
plot_intro(flux_df)
plot_missing(flux_df)
plot_bar(flux_df)
plot_histogram(flux_df)
plot_qq(flux_df)
plot_correlation(flux_df)
```



# Daily

## Munge & info

```{r}
time_daily <- daily$dim$time$vals
time_unit_daily <- daily$dim$time$units

var_names_daily <- names(daily$var)
## var_names_daily

for (i in var_names_daily){
  name <- paste("", i, sep = "")
  assign(name, ncvar_get(daily, varid = i))
}

daily_df <- data.frame(lapply(mget(var_names_daily), as.vector))
daily_df <- cbind(time_daily, daily_df)

daily_df$time_daily <- as.POSIXct("2000-01-01 12:00:00", tz="UTC") + (daily_df$time_daily)
```

bkd1d: daily background and daily averages
avg1m: XRS irradiances at 1-min cadence
xrsa_coverage: ikely refers to the extent or range of solar X-ray emissions that a specific instrument, such as an X-ray solar spectrometer, is capable of detecting or measuring. ORRR  In some cases, "XRS Coverage" could also refer to the time coverage of X-ray observations. This would specify the duration of time during which the instrument collects data during a given observation or data collection period.


## EDA

```{r}
gp2 <- ggplot(data = daily_df, aes(x=time_daily)) +
  geom_line(aes(y=bkd1d_xrsa_flux), color = "red", alpha = 0.2) + 
  geom_line(aes(y=avg1d_xrsa_flux), color = "darkred", alpha = 0.2) + 
  geom_line(aes(y=bkd1d_xrsb_flux), color = "blue", alpha = 0.2) + 
  geom_line(aes(y=avg1d_xrsb_flux), color = "darkblue", alpha = 0.2) + 
  theme_minimal()

gp2

ggplotly(gp2)
```


```{r}
introduce(daily_df)
plot_intro(daily_df)
plot_missing(daily_df)
plot_bar(daily_df)
plot_histogram(daily_df)
plot_qq(daily_df)
plot_correlation(daily_df)
```


# Flare

## Munge & info

```{r}
var_names_flare <- names(flare$var)

flare$var$flloc_hg$longname
flare$var$flloc_hg$units

for(i in var_names_flare){
  print(paste0(i, ": ", flare$var[[i]]$longname, "(", flare$var[[i]]$units, ")"))
  # print(flare$var[[i]]$longname)
  # print(flare$var[[i]]$units)
  # print(flare$var[[i]]$prec)
}
```


Stonyhurst/heliographic (lon, lat)
Carrington (lon, lat)
heliocentric-radial (R, θ) 
heliocentric Cartesian (x,y) coordinates
The solar P-angle and apparent solar angular radius

```{r}
time_flare <- flare$dim$time$vals
time_unit_daily <- flare$dim$time$units

time_flare <- as.POSIXct("2000-01-01 12:00:00", tz="UTC") + (time_flare)

var_names_flare <- names(flare$var)
## var_names_daily

for (i in var_names_flare){
  name <- paste("", i, sep = "")
  assign(name, ncvar_get(flare, varid = i))
}

for (i in var_names_flare){
  if (class(mget(i)[[i]])[1] == "matrix"){
    assign(i, t(mget(i)[[i]]))
  }
}

flare_df <- data.frame(time_flare, mget(var_names_flare))
colnames(flare_df) <- c("time_flare", "flloc_hg_long", "flloc_hg_lat", 
                        "flloc_car_long", "flloc_car_lat", "flloc_r", 
                        "flloc_theta", "flloc_x", "flloc_y", "solar_p_angle", 
                        "solar_radius", "flare_id")

## View(flare_df)
```

## EDA

```{r}
names(flare_df)

ggplot(data = flare_df, aes(x=flloc_x, y=flloc_y)) +
  geom_point() +
  geom_point(aes(0,0), color = "red", size = 10) +
  labs(title = "Map of Solar Flare Location",
       x = "Heliocentric Cartesian (X)",
       y = "Heliocentric Cartesian (Y)") +
  theme_bw()

ggplot(data = flare_df, aes(x=flloc_hg_lat, y=flloc_hg_long)) +
  geom_point() +
  geom_point(aes(0,0), color = "red", size = 10) +
  labs(title = "Map of Solar Flare Location",
       x = "Heliocentric Cartesian (X)",
       y = "Heliocentric Cartesian (Y)") +
  theme_bw()

ggplot(data = flare_df, aes(x=flloc_car_lat, y=flloc_car_long)) +
  geom_point() +
  geom_point(aes(0,0), color = "red", size = 10) +
  labs(title = "Map of Solar Flare Location",
       x = "Heliocentric Cartesian (X)",
       y = "Heliocentric Cartesian (Y)") +
  theme_bw()
```



# NOTES::

Figure out how long the flares are so that we can choose what kind of data (sec, min, hour, etc)

1. Equipments
  1. GOES -- Satelites (16,17,18) located at la grange point somewhere
      Generally the newest satelite set as primary
      measures flux
      other satelites can grab and observe the data
      1. Sensor: XRS --> X-ray sensor
  2. SDO -- Solar Dinamics Observatory
    1. AIA -- Camera that takes images at specific cycle of time
2. Sun
  Info
    photospehere --> hot but not that hot
    chromosphere --> target of interest
    corona --> target of interest
    further away, hotter it is (photo, chromo, corona from least to hottest)
  ARS
    Complex topography of magnetic field
    can observe active regions because of plasma coming out
    when flare goes off --> magnetic reconnection event
      magnetic fields are twisting and coming together, will snap and comes
      back together, peaks and rejoins from seconds to minutes (very quick)
    When flare goes off, changes the magnetic field from the reconnection  
    flares and active regions are correlated
    location matter because "prominence?" can be directed on 3d but image is 2d
3. Light
  Particle and/or wave
  Based on wavelength, see different colors and also have different energy
    primary looking at x-ray --> high energy
  Looking at light and its intensity (spectra)
  flux/integrated flux
    flux (W/m^2) (energy/sec/cm^2) --> vector field (energy per second per area)
      energy fluctuatition included
    integrated flux --> just integrate to get all energy amount
      simple calculation of how much energy it sends off --> sign of flare, but
      not sure where it would be
      
KEY POINT: DETECT FLARE (level of flare is a lot less important)
  
  
# 7 days work

## Load Data

```{r}
text <- "day"
for (i in 1:7){
  name <- paste0(text,i)
  file_dir <- "/Users/welpp/Desktop/Practical Data Science/Data/Temp Data/"
  pt1 <- "sci_xrsf-l2-flx1s_g16_d2023010"
  ptend <- "_v2-2-0.nc"
  file_loc <- paste0(file_dir, pt1, i, ptend)
  # print(i)
  # print(file_loc)
  assign(name, nc_open(file_loc))
}
# print(file)
```

## to df (seconds)

### function

```{r}
make_df_seconds <- function(file){
  time_flux <- file$dim$time$vals
  time_flux <- as.POSIXct("2000-01-01 12:00:00", tz="UTC") + (time_flux)
  time_unit_flux <- file$dim$time$units
  
  var_names <- names(file$var)
  
  var_names_file <- var_names[-c(15,16)]
  
  for (i in var_names_file){
    name <- paste("", i, sep = "")
    assign(name, ncvar_get(file, varid = i))
  }
  
  
  file_df <- data.frame(lapply(mget(var_names_file), as.vector))
  file_df <- cbind(time_flux, file_df)
  
  return(file_df)
}
```

## Comb

```{r}
# test1 <- make_df_seconds(day1)

for (i in 1:7){
  title <- paste0("df_day", i)
  file_name <- paste0("day",i)
  assign(title, make_df_seconds(get(file_name)))
}

df_week <- rbind(df_day1,df_day2,df_day3,df_day4,df_day5,df_day6,df_day7)
```

```{r}
fwrite(df_week, file = "/Users/welpp/Desktop/Practical Data Science/Data/Temp Data/df_week.csv")
```

